State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2016-02-15 draft.tex

\begin{cor}
Let $c_1$, $c_2$ and $c_3$ denote respectively the radii of: %
the largest ball centered on the origin contained in $\mathcal{X}$, 
%
the smallest ball centered on the origin that contains $\mathcal{P}_n$, and
%
the smallest ball centered on the origin that contains $\mathcal{V}_1(x)$ for all $x\in\mathcal{X}$.
%
If $c_i > (1-\rho)^{-1}c_3$ for $i=1,2$, then $\mathcal X^\infty = \mathcal X_M$ where
\begin{equation}\label{eq:iteration:cbound}
M = \max \biggl\{ n , 
\todo{Mark:log:bounds}{
\biggl\lceil \log_{\rho}\Bigl(\frac{c_1-(1-\rho)^{-1}c_3}{c_2-(1-\rho)^{-1}c_3}\Bigr)\biggr\rceil -1 \biggr\}}.
\end{equation}
\end{cor}
%

\begin{proof}
\todo{Manuel:proof:rewritten}{
Iteration~\eqref{eq:Xk:iteration} can be defined as $\mathcal X_{k+1} = \mathcal X_k\cap\mathcal D_{k+1}^\prime$ with $\mathcal X_0=\mathcal X$ where
$\mathcal D_k^\prime$ is defined by 
%
$$
\mathcal D_k^\prime = \{x\in\mathcal X_{k-1}:\{\Psi x\}\oplus\mathcal V(x)\subseteq \mathcal D_{k-1}^\prime\}
$$
%
and initialised as $\mathcal D_0^\prime=\mathcal X$.
%
It follows from the definition that $\mathcal X_k\subseteq\mathcal X_0=\mathcal X$ for all $k\in\mathbb N$.
%
Due to the fact that we chose~$c_3$ such that $\mathcal V(x)\subseteq c_3\mathcal E$ for all $x\in\mathcal X$ this also holds for all $x\in\mathcal X_k$.
%
We argue inductively: Clearly every $x$ such that $\{\rho x\}\oplus c_3\mathcal E\subseteq c_1\mathcal E$ also satisfies $\{\Psi x\}\oplus \mathcal V(x)\subseteq c_3\mathcal E \subseteq \mathcal X_0$, but the first condition is equivalent to $x\in\rho^{-1}(c_1\mathcal E\ominus c_3\mathcal E)=\rho^{-1}(c_1-c_3)\mathcal E$.
%
It follows that the ball of radius $\rho^{-1}(c_1-c_3)$ is contained in $\mathcal D_1^\prime$, we continue by determining the largest ball contained in $\mathcal D_2^\prime$ in the same fashion.
%
All points that satisfy $\{\rho x\}\oplus c_3\mathcal E \subseteq \rho^{-1}(c_1-c_3)\mathcal E$ also satisfy $\{\Psi x\}\oplus\mathcal V(x)\subseteq \mathcal D_2^\prime$ and so on.
%
Recursively we derive a ball for all subsequent $k$ such that $r_k\mathcal E\subseteq\mathcal D_k^\prime$, this radius is given by $r_k = \rho^{-k}(c_1-c_3\sum_{l=0}^{k-1}\rho^l) = \rho^{-k}(c_1-c_3\frac{1-\rho^k}{1-\rho})$.
%
Since $\mathcal X_k$ is defined as an intersection with the previous iterate the set can not change as soon as the inner ball has \emph{outgrown} any ball that contains $\mathcal X_k$.
%
We know that $\mathcal X_k\subseteq\mathcal P_n\subseteq c_2\mathcal E$ for all $k\geq n$ so that we have that $\mathcal X_k = \mathcal X_{k+1}=\mathcal X^\infty$ no later than the smallest $k\in\mathbb N$ such that $k\geq n$ and $c_2<r_k$, bound~\eqref{eq:iteration:cbound} follows from:
\[
\rho^k(c_2-\frac{c_3}{1-\rho})<c_1-\frac{c_3}{1-\rho}
\]
To preserve the orientation of the inequality we require $c_2-c_3(1-\rho)^{-1}>0$ and in order to obtain a positive argument in the logarithm we also require $c_1-c_3(1-\rho)^{-1}>0$.
%
This proves the assertion.
}
% \todo{Mark:proof:cor15}{%
% \def\X{\mathcal{X}}%
% \def\D{\mathcal{D}}%
% \def\V{\mathcal{V}}%
% \def\E{\mathcal{E}}%
% %
% The iteration (\ref{eq:Xk:iteration}) can be defined  equivalently as $\X_0=\X$ and $\X_k = \X_{k-1} \cap \D_k^\prime$ for $k=1,2,\ldots$, with
% \[
% \D_k^\prime = \bigl\{ x\in\X_{k-1} : \{\Psi x\} \oplus \V(x) If \subseteq \D_{k-1}^\prime\}
% \]
% for $k=1,2,\ldots$ and $\D_0^\prime=\X$. Clearly $\X_k\subseteq \X$ for all $k$, and since $V_1(x)\subseteq c_3\E$ for all $x\in\X$ (where $\E = B_1(0)$), it follows that $\D^\prime_k \supseteq \Psi^{-1}(\D_{k-1}^\prime \ominus c_3\E)$ and 
% \[
% \D_k^\prime 
% \supseteq 
% %\Psi^{-k}\ominus \bigoplus_{i=0}^k c_3 \Psi^{-i}\E=
% \Psi^{-k} \Bigl[ \X \ominus \bigoplus_{i=0}^{k-1} c_3\Psi^i\E \Bigr]
% \supseteq 
% \Bigl[ c_1 - \Bigl(\frac{1-\rho^k}{1-\rho} \Bigr) c_3\Bigr] \rho^{-k}\mathcal{E} 
% \]
% since $\X\subseteq c_1\E$. 
% %
% Therefore $\D_k^\prime\neq \emptyset$ for all $k$ if $c_1 > (1-\rho)^{-1}c_3$, and in this case, since $\X_{k-1} \subseteq \mathcal{P}_n\subseteq c_2\E$ for all $k\geq n+1$, we have $\X_{k-1}\subseteq \D_k^\prime$ if $c_2\rho^k \leq c_1 - c_3(1-\rho^k)/(1-\rho)$. 
% %
% Hence $\X^\infty=\X_M$, where $M$ is 
% %given by (\ref{eq:iteration:cbound}).}
% the smallest integer such that $k= M+1$ satisfies this condition, which is given by (\ref{eq:iteration:cbound})
% since $c_2>(1-\rho)^{-1}c_3$ is assumed.}

>>>>

\begin{cor}
Let $c_1$, $c_2$ and $c_3$ denote respectively the radii of: %
the largest ball centred on the origin contained in $\mathcal{X}$, 
%
the smallest ball centred on the origin that contains $\mathcal{P}_n$, and
%
the smallest ball centred on the origin that contains $\mathcal{V}_1(x)$ for all $x\in\mathcal{X}$.
%
If $c_i > (1-\rho)^{-1}c_3$ for $i=1,2$, then $\mathcal X^\infty = \mathcal X_M$ where
\begin{equation}\label{eq:iteration:cbound}
M = \max \biggl\{ n , 
\todo{Mark:log:bounds}{
\biggl\lceil \log_{\rho}\Bigl(\frac{c_1-(1-\rho)^{-1}c_3}{c_2-(1-\rho)^{-1}c_3}\Bigr)\biggr\rceil -1 \biggr\}}.
\end{equation}
\end{cor}
%
\todo{Manuel:proof:rewritten}{
Iteration~\eqref{eq:Xk:iteration} can be defined as $\mathcal X_{k+1} = \mathcal X_k\cap\mathcal D_{k+1}^\prime$ with $\mathcal X_0=\mathcal X$ where
$\mathcal D_k^\prime$ is defined by 
$$
\mathcal D_k^\prime = \{x\in\mathcal X_{k-1}:\{\Psi x\}\oplus\mathcal V(x)\subseteq \mathcal D_{k-1}^\prime\}
$$
and initialised as $\mathcal D_0^\prime=\mathcal X$.
It follows from the definition that $\mathcal X_k\subseteq\mathcal X_0=\mathcal X$ for all $k\in\mathbb N$.
Due to the fact that we chose~$c_3$ such that $\mathcal V(x)\subseteq c_3\mathcal E$ for all $x\in\mathcal X$ this also holds for all $x\in\mathcal X_k$.
We argue inductively: Clearly every $x$ such that $\{\rho x\}\oplus c_3\mathcal E\subseteq c_1\mathcal E$ also satisfies $\{\Psi x\}\oplus \mathcal V(x)\subseteq c_3\mathcal E \subseteq \mathcal X_0$, but the first condition is equivalent to $x\in\rho^{-1}(c_1\mathcal E\ominus c_3\mathcal E)=\rho^{-1}(c_1-c_3)\mathcal E$.
It follows that the ball of radius $\rho^{-1}(c_1-c_3)$ is contained in $\mathcal D_1^\prime$, we continue by determining the largest ball contained in $\mathcal D_2^\prime$ in the same fashion.
The iteration (\ref{eq:Xk:iteration}) can be defined  equivalently as $\X_0=\X$ and $\X_k = \X_{k-1} \cap \D_k^\prime$ for $k=1,2,\ldots$, with
\D_k^\prime = \bigl\{ x\in\X_{k-1} : \{\Psi x\} \oplus \V(x) \subseteq \D_{k-1}^\prime\}
for $k=1,2,\ldots$ and $\D_0^\prime=\X$. Clearly $\X_k\subseteq \X$ for all $k$, and since $V_1(x)\subseteq c_3\E$ for all $x\in\X$ (where $\E = B_1(0)$), it follows that $\D^\prime_k \supseteq \Psi^{-1}(\D_{k-1}^\prime \ominus c_3\E)$ and 
\D_k^\prime 
\supseteq 
%\Psi^{-k}\ominus \bigoplus_{i=0}^k c_3 \Psi^{-i}\E=
\Psi^{-k} \Bigl[ \X \ominus \bigoplus_{i=0}^{k-1} c_3\Psi^i\E \Bigr]
\supseteq 
\Bigl[ c_1 - \Bigl(\frac{1-\rho^k}{1-\rho} \Bigr) c_3\Bigr] \rho^{-k}\mathcal{E} 
since $\X\subseteq c_1\E$. 
All points that satisfy $\{\rho x\}\oplus c_3\mathcal E \subseteq \rho^{-1}(c_1-c_3)\mathcal E$ also satisfy $\{\Psi x\}\oplus\mathcal V(x)\subseteq \mathcal D_2^\prime$ and so on.
Recursively we derive a ball for all subsequent $k$ such that $r_k\mathcal E\subseteq\mathcal D_k^\prime$, this radius is given by $r_k = \rho^{-k}(c_1-c_3\sum_{l=0}^{k-1}\rho^l) = \rho^{-k}(c_1-c_3\frac{1-\rho^k}{1-\rho})$.
Since $\mathcal X_k$ is defined as an intersection with the previous iterate the set can not change as soon as the inner ball has \emph{outgrown} any ball that contains $\mathcal X_k$.
We know that $\mathcal X_k\subseteq\mathcal P_n\subseteq c_2\mathcal E$ for all $k\geq n$ so that we have that $\mathcal X_k = \mathcal X_{k+1}=\mathcal X^\infty$ no later than the smallest $k\in\mathbb N$ such that $k\geq n$ and $c_2<r_k$, bound~\eqref{eq:iteration:cbound} follows from:
\rho^k(c_2-\frac{c_3}{1-\rho})<c_1-\frac{c_3}{1-\rho}
To preserve the orientation of the inequality we require $c_2-c_3(1-\rho)^{-1}>0$ and in order to obtain a positive argument in the logarithm we also require $c_1-c_3(1-\rho)^{-1}>0$.
This proves the assertion.
% \todo{Mark:proof:cor15}{%
% \def\X{\mathcal{X}}%
% \def\D{\mathcal{D}}%
% \def\V{\mathcal{V}}%
% \def\E{\mathcal{E}}%
% The iteration (\ref{eq:Xk:iteration}) can be defined  equivalently as $\X_0=\X$ and $\X_k = \X_{k-1} \cap \D_k^\prime$ for $k=1,2,\ldots$, with
% \[
% \D_k^\prime = \bigl\{ x\in\X_{k-1} : \{\Psi x\} \oplus \V(x) If \subseteq \D_{k-1}^\prime\}
% \]
% for $k=1,2,\ldots$ and $\D_0^\prime=\X$. Clearly $\X_k\subseteq \X$ for all $k$, and since $V_1(x)\subseteq c_3\E$ for all $x\in\X$ (where $\E = B_1(0)$), it follows that $\D^\prime_k \supseteq \Psi^{-1}(\D_{k-1}^\prime \ominus c_3\E)$ and 
% \[
% \D_k^\prime 
% \supseteq 
% %\Psi^{-k}\ominus \bigoplus_{i=0}^k c_3 \Psi^{-i}\E=
% \Psi^{-k} \Bigl[ \X \ominus \bigoplus_{i=0}^{k-1} c_3\Psi^i\E \Bigr]
% \supseteq 
% \Bigl[ c_1 - \Bigl(\frac{1-\rho^k}{1-\rho} \Bigr) c_3\Bigr] \rho^{-k}\mathcal{E} 
% \]
% since $\X\subseteq c_1\E$. 
% Therefore $\D_k^\prime\neq \emptyset$ for all $k$ if $c_1 > (1-\rho)^{-1}c_3$, and in this case, since $\X_{k-1} \subseteq \mathcal{P}_n\subseteq c_2\E$ for all $k\geq n+1$, we have $\X_{k-1}\subseteq \D_k^\prime$ if $c_2\rho^k \leq c_1 - c_3(1-\rho^k)/(1-\rho)$. 
% Hence $\X^\infty=\X_M$, where $M$ is 
% %given by (\ref{eq:iteration:cbound}).}
% the smallest integer such that $k= M+1$ satisfies this condition, which is given by (\ref{eq:iteration:cbound})
% since $c_2>(1-\rho)^{-1}c_3$ is assumed.}
